---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ml

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/poissonconsulting/ml.svg?branch=master)](https://travis-ci.com/poissonconsulting/ml)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/poissonconsulting/ml?branch=master&svg=true)](https://ci.appveyor.com/project/poissonconsulting/ml)
[![Codecov test coverage](https://codecov.io/gh/poissonconsulting/ml/branch/master/graph/badge.svg)](https://codecov.io/gh/poissonconsulting/ml?branch=master)
[![License: MIT](https://img.shields.io/badge/License-MIT-green.svg)](https://opensource.org/licenses/MIT)
<!-- [![Tinyverse status](https://tinyverse.netlify.com/badge/ml)](https://CRAN.R-project.org/package=ml) -->
<!-- [![CRAN status](https://www.r-pkg.org/badges/version/ml)](https://cran.r-project.org/package=ml) -->
<!-- ![CRAN downloads](https://cranlogs.r-pkg.org/badges/ml) -->
<!-- badges: end -->

`ml` is an R package to perform Maximum Likelihood analysis using R expressions.

It is designed to be simple but flexible.

## Demonstration

### Flexible Analyses

```{r}
library(ml)

# the R expression is currently passed as unparsed text
# it should evaluate to the log likelihood
expr <- "sum(dnorm(len, mu, b[1,1] + b[1,2], log = TRUE))"

# the list of parameters can include arrays and matrices
# the values are the initial values (NAs are fixed at 0)
pars <- list(mu = 20, b = matrix(c(8, NA), ncol = 2))

# data can be a data.frame or list of numeric atomic objects
data <- datasets::ToothGrowth

# perform the analysis
analysis <- ml_analyse(expr, pars = pars, data = data)

# the coefficient table includes svalues (in place of pvalues).
ml_coef_table(analysis, constant = NA)
```

## Convergence

No convergence, no problem!

```{r}
analysis <- ml_analyse("1", pars = pars, data = data)
ml_converged(analysis)
ml_coef_table(analysis, constant = NA)
```

### stats generics

Basic stats package generics are also implemented.

```{r}
coef(analysis)
logLik(analysis)
AIC(analysis)
```

## Installation

<!-- To install the latest release from [CRAN](https://cran.r-project.org) -->
```{r, eval=FALSE, echo=FALSE}
install.packages("ml")
```

To install the developmental version from [GitHub](https://github.com/poissonconsulting/ml)
```{r, eval=FALSE}
# install.packages("remotes")
remotes::install_github("poissonconsulting/ml")
```

To install the latest developmental release from the Poisson drat [repository](https://github.com/poissonconsulting/drat)
```{r, eval=FALSE}
# install.packages("drat")
drat::addRepo("poissonconsulting")
install.packages("ml")
```

## Contribution

Please report any [issues](https://github.com/poissonconsulting/ml/issues).

[Pull requests](https://github.com/poissonconsulting/ml/pulls) are always welcome.

Please note that this project is released with a [Contributor Code of Conduct](https://github.com/poissonconsulting/ml/blob/master/CODE_OF_CONDUCT.md).
By contributing, you agree to abide by its terms.
